Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-07 doc/ms.tex
Cite Matt and Renate

In astronomy, time series analysis of variable sources has often been performed
in the frequency domain \citep[e.g.][]{lomb, hatzes, helio}. However,
a number of researchers have applied existing time series models from
statistics \citep{brockwell_davis} or custom-made models to infer parameters
directly from the time series data, without any use of the frequency domain
\citep[e.g.][]{gregory_loredo, gregory, kelly, brewer_stello, farr}.

@@

>>>>

In astronomy, time series analysis of variable sources has often been performed
in the frequency domain \citep[e.g.][]{lomb, hatzes, helio}. However,
a number of researchers have applied existing time series models from
statistics \citep{brockwell_davis} or custom-made models to infer parameters
directly from the time series data, without any use of the frequency domain
\citep[e.g.][]{gregory_loredo, gregory, kelly, brewer_stello, farr, edwards}.

@@

\bibitem[Edwards et al.(2015)]{edwards}
Edwards, Matthew C., Renate Meyer, and Nelson Christensen.
``Bayesian semiparametric power spectral density estimation with applications
in gravitational wave data analysis.'' Physical Review D 92, no. 6 (2015): 064011.
